Contracts for Contracts

### 2023-04-21 paper.tex
thoughts

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We propose an conservative linguistic extension to Solidty,
    namely the temporal and higher-order contracts to improve the safety and
    reliability.
  \item We present the core language ``Contract Solidity'' with our
    proposed extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal, therefore practical to use.
\end{itemize}

>>>>

% second-class contracts

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We propose a specification of behavior contracts for expressing and
    enforcing higher-order and temporal properties for smart contracts.
  \item We design a language extension of behavior contracts for Solidty,
    demonstrate its use cases through extensive examples,
    and how it can improve the safety and reliability.
  \item We present the core language ``Contract Solidity'' with our proposed
    extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world attacks and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal, therefore practical to use.
\end{itemize}
